Constraints on Assembly Bias from Galaxy Clustering

### 2016-06-13 ms.tex
Edited section 3.1

Our work is a re-analysis of the SDSS DR7 data that 
overcomes numerous shortcomings of previous
analyses. In particular, we use direct population of galaxies in a
cosmological simulation so that delicate issues present in analytic
modeling, such as scale-dependent halo bias, are treated exactly.  The
simulation we use is based on the latest Planck cosmological
parameters \citep{planck13}, updating previous work. 
Furthermore, many important
differences between this work and the previous analysis by
\citet{zehavi_etal11} result from the fact that the Monte Carlo Markov
Chains used in \citet{zehavi_etal11} were not converged 
(Z. Zheng, private communication). Therefore,
{\em our analysis supersedes previous work even in the case of
standard halo occupation models}.

>>>>

This work presents a re-analysis of the SDSS DR7 data that 
overcomes numerous shortcomings of previous analyses. 
Our analysis improvements stem primarily from our 
directly populating mock galaxy catalogs into a cosmological simulation, 
whereas previous analyses relied upon analytical fitting functions 
with parameters calibrated against a suite of simulations. 
In direct mock population, delicate issues present in analytic
modeling, such as scale-dependent halo bias and halo exclusion, are treated exactly.  
Our approach also provides a natural framework for studying models of assembly bias, 
since we can use the exact clustering properties of simulated halos as a function of 
any arbitrary halo properties in the catalog. With direct mock population, 
systematic uncertainty in the model is limited to 
the sample variance of the simulated box, 
errors related to insufficient numerical resolution, 
and numerical inaccuracies of halo-finding (e.g., over-merging).

In addition to improvements from direct mock population, 
the simulation we use is based on the latest Planck cosmological
parameters \citep{planck13}, updating previous work. 
Furthermore, many important
differences between this work and the previous analysis by
\citet{zehavi_etal11} result from the fact that the Monte Carlo Markov
Chains used in \citet{zehavi_etal11} did not sufficiently sample the 
posterior distribution (Z. Zheng \& I. Zehavi, private communication).  Therefore,
{\em our analysis supersedes previous work even in the case of
standard halo occupation models}.
